\documentclass{article}[12pt]
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{times}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\def \R {\mathbb R}
\def \imp {\Longrightarrow}
\def \eps {\varepsilon}
\def \Inf {{\sf Inf}}
\newenvironment{proof}{{\bf Proof.  }}{\hfill$\Box$}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{claim}{Claim}[section]
\setlength {\parskip}{2pt}
\setlength{\parindent}{0pt}

\newcommand{\headings}[4]{\noindent {\bf CS154: Introduction to Automata and
Complexity Theory} \hfill {Winter 2015} \\
{\noindent {\bf Homework} #1} \hfill {{\bf Due Date:} #2} \\

\rule[0.1in]{\textwidth}{0.025in}
}

\newcommand{\klnote}[1]{{\color{red} #1}}
\newcommand{\klsout}[1]{{\color{red} \sout{#1}}}

% My custom stuff:
\usepackage{tikz,enumerate}
\newcommand{\soln}{\textbf{\newline Solution: }}
\renewcommand{\emptyset}{\varnothing}
\newcommand{\xor}{\bigoplus}

\title{Programming Project 1 - Short Answers}
\author{Leo Martel, Christine Li}
\date{Friday, Feb 13, 2015}

\begin{document}

\maketitle

\begin{enumerate}[1.]
\item The adversary is prevented from learning information about the
  lengths of the passwords because the passwords are all padded to 64
  bytes (maximum password length), salted with $HMAC(domain)$, which is
  always 256 bits, and finally salted with a random additional salt of
  constant length (64 bytes). AES is a block cipher, so given a
  fixed-size input will produce a fixed-size output. Therefore the
  encrypted passwords are all the same length, and no length
  information is leaked.

\item We use the HMAC'd domain (the keyring key) as part of the
  password (keyring value) salt. When $get(domain)$ is called, the
  salted password is decrypted and the stored domain is compared to
  the parameter. If the domain does not match, we throw a tampering
  exception. Since a key-value store by definition only contains one
  password for each domain, swap attacks are impossible.

\item Yes, the trusted location is necessary. If we store the digest on disk, an adversary could modify the database and then modify the digest to match, causing our integrity check to produce a false positive. For example, the adversary could successfully execute a rollback attack by rolling back both the database and the digest to corresponding earlier versions.

\item Using another MAC could jeopardize the security of this system. Specifically, as shown in class CBC-MAC is secure only for fixed-length plaintexts. Domains are not fixed length. They can be arbitrarily long (and the assignment specification doesn't provide a maximum length), so padding is insufficient. Different-length plaintexts produce different-length ciphertexts, leaking information about domain length; in addition, an adversary can win the existential forgery game by submitting plaintexts of varying length.

\item We could pad the password manager with bogus entries such that it is always at its maximum capacity (or at some practical “large enough” capacity). Before encryption, we could put in an indicator in either the URL or password ($fake||http://…$ or $real||http://…$) that indicates whether the entry is real or fake. These prefixes would not jeopardize security because we add them before running through HMAC. When adding a new entry, we could iterate through all of the keys until we find a fake one, then delete it. Then, we could add in our new entry to bring the total record count back up to the maximum.


\end{enumerate}

\end{document}
